\input preamble

The emergence of consciousness from study and reflection and
understanding brings the spirit to the tranquility that can be shared
as fellowship.  The joy of productivity and creativity that is genuine
is human and generous and efficient.

In my own journey I've travelled through territories of learning
including the study of power in the universal human experience.  The
human experience has accumulated and been lost variously through the
centuries.  As read from Krishna Consciousness, the facilities of the
human being establish the right of passage through the territories of
the human experience.  As read from Science, the experiment is
necessary to the benefit of development.  And as read from Jesus
Christ, the gift of love is divine grace: discard all that would
inhibit its revelation.

The inhibition of love is the quarry of trust.  I can trust that I
will not be inhibited from my own occupations of life and development.
It's hard to do so in person when the critical subjects of thought are
excluded from conversation.  The dimensions and magnitudes of
relationships depend on trust.  While it is silent or indirect under
the sublimation of desire of friendship or other forms or derivatives
of relationship, we degrade trust.  In the exploration of character we
trade trust for learning to arrive at the cusp of communication.  We
experience security and insecurity within the dimensions or channels
of communication, and err at the generalisation of this experience to
trust and relationship.  That is, the cost of clarity in communication
is far more dear than one might realize for many years.  The avenue to
the retrieval of life's journey from the vagaries of society is first
the dedication to trustworthy communication and second the commitment
to education and scholarship.

\bye
