\input preamble

{\global\let\reviews = \rightleftharpoons}
{\global\let\accepts = \leftarrow}
{\global\let\rejects = \rightarrow}

On another level of abstraction, the equation of being
$$\displaylines{ \psi = \alpha \times \beta \times \gamma, \cr \psi
 = \alpha + \beta + \gamma,}$$ can be understood to represent inner
 ($\alpha$), outer ($\beta$), and social consciousness ($\gamma$).

That social consciousness exists on par with inner and outer
consciousness is omitted for brevity.  I propose as an understood
metaphysical fact that the inner consciousness has no awareness that
is not derived from the outer consciousness.

$$ \alpha \accepts \beta $$

And derive from this fact that the outer consciousness serves as the
eyes of the inner consciousness, abstract from the immediacy of
intellect.  That is, ($1$) the inner consciousness sees the outer
consciousness.  And ($2$), the inner consciousness reviews and accepts
or rejects {\it beliefs} from the outer consciousness.

The known phenomenon ranges from the internalization of understanding
as comprehension

$$ \Re\alpha \accepts \Re\beta,$$

to the most profound {\it acceptance} of issues of faith and intimacy

$$ \aleph\alpha \accepts \aleph\beta.$$

The inner consciousness regularly {\it rejects} comprehension or
belief that violate the self

$$\displaylines{  \Re\alpha \rejects \Re\beta, \cr
 \aleph\alpha \rejects \aleph\beta,}$$

which may produce an emotive sense or reaction, or even a
psychological disorder within the processes of acceptance and
rejection

$$\displaylines{  \Re\alpha \reviews \Re\beta, \cr
 \aleph\alpha \reviews \aleph\beta.}$$

\bigskip

The facility to accept or reject issues of comprehension, faith and
intimacy within the self is profound and remote from the intellect.

The structure of self serves to construct a coherent individual
character, and to perceive the characters of other individuals.

A metaphysical epistemology in mathematical logic serves conscience
and consciousness.



\bye
